### 2017-05-12 manuscript/usses_water_ms.Rmd
getting some citations right

### Data Analysis
####  ANPP and Ecosystem Stability
We used ANOVA with treatment, year, and treatment$\times$year terms to test the effects of the treatments on ANPP over the course of the five year experiment.
To test for within-year differences of ANPP among treatments, we fit ANOVAs independently for each year with treatment terms only.
We used the \texttt{lm()} function in \texttt{R} [v3.3.2, @R2016] to fit the models, and the \texttt{anova()} function to extract sums-of-squares tables.

@@

inyear_caption <- "ANOVA for treatment effects on ANPP for each year of the experiment."
print(xtable(inyear_anova, caption = inyear_caption),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment=FALSE,
      size="normalsize")
```

>>>>

### Data Analysis
####  ANPP and Ecosystem Stability
We used ANOVA with treatment, year, and treatment$\times$year terms to test the effects of the treatments on ANPP over the course of the five year experiment.
To test for within-year differences of ANPP among treatments, we fit ANOVAs independently for each year with treatment terms only.
We used the \texttt{lm()} function in \texttt{R} [v3.3.2, @R2016] to fit the models, and the \texttt{Anova()} function from the \texttt{car} package [@Fox2011] to extract sums-of-squares tables with Type II tests.

@@

inyear_caption <- "ANOVA for treatment effects on ANPP for each year of the experiment."
print(xtable(inyear_anova, caption = inyear_caption, digits = 2),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment = FALSE,
      size = "normalsize")
```
